### 2022-05-17 Publish Paper/manuscript_title_etc.tex
Update Paper
Update Publish Paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 2. Define Title
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERTITLE}{Skin Cancer Classification using Soft Attention and Metadata Concatenance}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 5. Define Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERABSTRACT}{
Recent estimates are that about 150 million children under five years of age are stunted, with substantial negative consequences for their schooling, cognitive skills, health, and economic productivity. Therefore, understanding what determines such growth retardation is significant for designing public policies that aim to address this issue. We build a model for nutritional choices and health with reference-dependent preferences. Parents care about the health of their children relative to some reference population. In our empirical model, we use height as the health outcome that parents target. Reference height is an equilibrium object determined by earlier cohorts' parents' nutritional choices in the same village. We explore the exogenous variation in reference height produced by a protein-supplementation experiment in Guatemala to estimate our model’s parameters. We use our model to decompose the impact of the protein intervention on height into price and reference-point effects. We find that the changes in reference points account for 65\% of the height difference between two-year-old children in experimental and control villages in the sixth annual cohort born after the initiation of the intervention.}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 2. Define Title
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERTITLE}{Skin Cancer Classification using Soft Attention and Metadata}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 5. Define Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERABSTRACT}{
Nowadays, the dramatic development of the big city and industrial field leads to a higher rate of skin disease because of polluted air. Moreover, in many developing countries, the hospital is being overloaded every single day by the huge number of the patient. They need a fast and accurate solution to diagnose skin disease before meeting the doctor or how to create an optimized and balanced model for skin lesion classification. After the literature review process, I found that there are many outstanding papers on both Deep Learning and Machine Learning. In Deep Learning, they often use transfer learning. Some new approaches are GradCam, Kernel Shap, Student and Teacher model. In Machine Learning, Random Forest, and Support Vector Machine are applied. The main focus of this research is to analyze the effect of metadata on the combination of the backbone model and the Soft-Attention layer. The soft-Attention layer is tested in a previous paper that improve the model performance. I also try some other combinations to construct an optimized model that can use on mobile phone. After the experiment process, I found out that metadata makes the performance of the model more balanced than in the previous paper. I also construct a model with the combination of MobileNetV3Large and Soft-Attention layer with image and metadata input with a bit lower accuracy but thirty times as fast as other combinations.
}
